Uncovering underlying high-level musical content in the time domain \\ \small Leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn deep audio embeddings with applications to MIR downstream tasks

### 2023-06-09 results/subsections/tables.tex
Updates from Overleaf

@@

\begin{table}[h]
\centering
\small
\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}p{4.5cm}XXXXX}
\toprule
\thead{\centering\textbf{Authors [Ref], Year}} & \thead{\centering\textbf{Input}} & \thead{\centering\textbf{Method}} & \thead{\centering\textbf{F-measure}} \\
\midrule
\addlinespace
Kaiser et al. \cite{27}, 2012 & SSM & Novelty measure  & 0.286 \\
\addlinespace
McFee \& Ellis \cite{20}, 2013 & MLS & Fisher’s Linear Discriminant  & 0.317 \\
\addlinespace
Nieto \& Bello \cite{28}, 2014 & MFCCs, chromas & Checkerboard-like kernel  & 0.299 \\
\addlinespace
Cannam et al. \cite{29}, 2015 & Timbre-type histograms & HMM  & 0.213 \\
\addlinespace
Nieto \cite{30}, 2016 & Constant-Q Transform Spectrogram & Linear Discriminant Analysis  & 0.299 \\
\addlinespace
Cannam et al. \cite{29}, 2017 & Timbre-type histograms & HMM  & 0.212 \\
\addlinespace
Turnbull et al. \cite{Turnbull2007ABOOSTING}, 2007 & MFCCs, chromas, spectrogram & Boosted Decision Stump  & 0.378 \\
\addlinespace
Sargent et al. \cite{34}, 2011 & MFCCs, chromas & Viterbi  & 0.356 \\
\addlinespace
Ullrich et. al \cite{22}, 2014 & MLS & CNN  & 0.465 \\
\addlinespace
Grill \& Schlüter \cite{4}, 2015 & MLS, SSLMs & CNN  & 0.523 \\
\addlinespace
Grill \& Schlüter \cite{GrillMUSICANNOTATIONS}, 2015 & MLS, PCPs, SSLMs & CNN  & 0.508 \\
\addlinespace
Hadria \& Peeterss \cite{35}, 2017 & MLS, SSLMs & CNN  & 0.291 \\
\bottomrule
\end{tabularx}
\caption[Baseline. State of the art table.]{Your Caption.}
\label{tab:my_label}
\end{table}

>>>>

SALAMI (Structural Analysis of Large Amounts of Music Information) is a project aiming to carry out extensive structural analyses on a wide variety of music, from Western pop to Indian classical, and from live to studio recordings \cite{Smith2011DESIGNANNOTATIONS}. Instead of traditional forms, the authors segment pieces into sections, combining perceptual, functional, and transcription analyses. Despite limitations, this approach offers a holistic and nuanced perspective on music structure.

@@

\begin{table}[h]
\centering
\small
\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}p{4.5cm}XXXXX}
\toprule
\thead{\centering\textbf{Authors [Ref], Year}} & \thead{\centering\textbf{Input}} & \thead{\centering\textbf{Method}} & \thead{\centering\textbf{F-measure}} \\
\midrule
\addlinespace
Kaiser et al. \cite{27}, 2012 & SSM & Novelty measure  & 0.286 \\
\addlinespace
McFee \& Ellis \cite{20}, 2013 & MLS & Fisher’s Linear Discriminant  & 0.317 \\
\addlinespace
Nieto \& Bello \cite{28}, 2014 & MFCCs, chromas & Checkerboard-like kernel  & 0.299 \\
\addlinespace
Cannam et al. \cite{29}, 2015 & Timbre-type histograms & HMM  & 0.213 \\
\addlinespace
Nieto \cite{30}, 2016 & Constant-Q Transform Spectrogram & Linear Discriminant Analysis  & 0.299 \\
\addlinespace
Cannam et al. \cite{29}, 2017 & Timbre-type histograms & HMM  & 0.212 \\
\addlinespace
Turnbull et al. \cite{Turnbull2007ABOOSTING}, 2007 & MFCCs, chromas, spectrogram & Boosted Decision Stump  & 0.378 \\
\addlinespace
Sargent et al. \cite{34}, 2011 & MFCCs, chromas & Viterbi  & 0.356 \\
\addlinespace
Ullrich et. al \cite{22}, 2014 & MLS & CNN  & 0.465 \\
\addlinespace
Grill \& Schlüter \cite{4}, 2015 & MLS, SSLMs & CNN  & 0.523 \\
\addlinespace
Grill \& Schlüter \cite{GrillMUSICANNOTATIONS}, 2015 & MLS, PCPs, SSLMs & CNN  & 0.508 \\
\addlinespace
Hadria \& Peeterss \cite{35}, 2017 & MLS, SSLMs & CNN  & 0.291 \\
\bottomrule
\end{tabularx}
\caption[Baseline. State of the art table.]{Your Caption.

SALAMI dataset

}
\label{tab:my_label}
\end{table}
